Resilience and Home-Space for WSTS

### 2024-01-09 diapo/presentation.tex
up

	$\to$ link between runs and runs of the completion (must define completion)

	$\to$ ideal decomposition of Bad

	$\to$ basis of Safe

	$\to$ coverability questions

	$\to$  resilience(s) can be reduced to coverability

@@

    \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Ingredient 3 (only for $k$-resilience)}

     \todo[inline,color=blue!20]{ 
  ... actually it is generally over now maybe we don't have to go into all the details here
}

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Result B}

 résultat sur la deuxième figure ?
 on signale juste le thm 8 en passant ?

     \todo[inline,color=blue!20]{    Result blabla are consequences of the paper    by Okzan so let's not delve into it.
    ( should still be quite precise about Okzan result and references)}

@@

>>>>

% 	$\to$ ideal decomposition of Bad

%	$\to$ basis of Safe

 	$\to$ resilience =$>$ infinite number of coverability questions

	$\to$ introduce the completion

	$\to$  here resilience =$>$ finite number of coverability questions

@@

    \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Ingredient 3}

 $\to$ consider max length of such coverability questions

  $\to$ answers {\sc Bounded resilience} and {\sc $k$-resilience} as well
     \todo[inline,color=blue!20]{ 
  ... actually it is generally over now maybe we don't have to go into all the details here
}

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{State Resilience when $\Safe = {\uparrow \Safe}$}

 % résultat sur la deuxième figure ?
 % on signale juste le thm 8 en passant ?

 %    \todo[inline,color=blue!20]{    Result blabla are consequences of the paper    by Okzan so let's not delve into it.
 %   ( should still be quite precise about Okzan result and references)}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Resilience $\ldots$}

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Resilience $\ldots$ for VASS}
